A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory

### 2020-04-28 Article_file_Source_reconstruction.tex
Updates from Overleaf

While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a).  In Figure \ref{fig2}(a) we show cross-section A-A from Figure \ref{fig1}(b). The source is produced by the piezoelectric actuator on the top surface of the steel plate causing elastodynamic spherical stress waves (colored) to propagate outwards. This wave-field is actually only used as a reference and is not representative of the source produced from the PZT actuator (determined later). The colored region in Figure \ref{fig2}(a) represents the velocity wave-field produced from a ball drop at the actuator location, which has been well-studied in recent years \citet{McLaskey2010, Wu2018, Wu2020}. In Figure \ref{fig2}(a), we show the ``toolchain'' that is used to process the seismic waves produced by the PZT actuator. The PZT actuator is used to produce a force $f_{j}\left( \mathbf{\xi}, \tau \right)$ on the top surface at a point $\mathbf{\xi}$ of the steel platen. A passive sensor, on the bottom surface at point $\mathbf{x}$, attempts to measure the theoretical displacements with time $u_{k}\left( \mathbf{x}, t \right)$. Green’s functions are a basic ingredient in the Knopoff--de Hoop representation theorem \citep{Burridge1964} is the solution to the elastic wave equation relating the elastic displacements to the source throughout he elastic half-space. Unfortunately, the passive sensors are unable to truly capture the theoretical displacements and will distort the measured signal $s(t)$ according to its instrument response $i_{k}(t)$.  In this study we consider the instrument response to include effects of the sensor, cabling and internal component of the data acquisition allowing for digitization of the signal.

@@

\section{Theory}
\label{theo}
We review the methodology that will model the forces produced by an active source piezoelectric transducer.  This methodology takes advantage of the theory surrounding elastodynamic wave propagation in an elastic medium.  We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. We assume that wave propagation can be adequately described by convolution with the Green's function and that each component in our analysis can be modeled as a linear-time invariant system.  We are assuming that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location. This so-called ``aperture'' effect is minimized by using the point contact conical PZT crystal but some deviations might be incurred.

>>>>

While more complex sources have been considered to model earthquakes, such as the single and double couple source \citet{Sato1972}, we believe the original problem studied by \citet{Lamb1904} -- elastic displacements resulting from a point force in/on a half space -- is sufficiently complex for capturing the behavior of the piezoelectric actuator depicted in Figure \ref{fig2}(a). In Figure \ref{fig2}(a), we show the cross-section A-A from Figure \ref{fig1}(b). The source is produced by pulsing the piezoelectric actuator on the top surface using the experimental facilities described in Figure \ref{fig1}. The impulsive actuation of the PZT crystal on the steel plate produces a rapid transient source causing elastodynamic stress waves to propagate outwards. In Figure \ref{fig2}, the coloured region represents a synthetic representation of the velocity wave-field and is only provided as a reference and is not representative of the source produced from the PZT actuator (which is to be determined later). For this example, we show the velocity wave-field produced from a ball drop at the same location as the PZT actuator location from numerical finite element simulations in ABAQUS.

The type of source creating the stress waves is important. \citet{Breckenridge1990} states that the ideal source is infinitesimal in size, has a force-time function of a step or delta function, and generates large amplitudes. He performed important study of a variety of sources including pencil lead fracture, capillary fracture, capacitive transducer, conical transducer, ball impact, spark, and high explosive, noting that each type is imperfect and has its trade offs. In this study, we look to aim to understand the PZT actuator (similar to conical transducer) which we can leverage to non-invasively study the \textit{in situ} absolute calibration conditions inside a less accessible experimental facility (e.g. trixaial pressure cell). To model the force-time function produced conical sensor, we first simplify the sequence of events and their components that link the source to the recorded signal.

In Figure \ref{fig2}(a), we show the ``toolchain'' that is used to process the seismic waves produced by the PZT actuator. The PZT actuator is used to produce a force $f_{j}\left( \mathbf{\xi}, \tau \right)$ on the top surface at a point $\mathbf{\xi}$ of the steel platen. A passive sensor, on the bottom surface at point $\mathbf{x}$, attempts to measure the theoretical displacements with time $u_{k}\left( \mathbf{x}, t \right)$. Green’s functions are a basic ingredient in the Knopoff--de Hoop representation theorem \citep{Burridge1964} is the solution to the elastic wave equation relating the elastic displacements to the source throughout he elastic half-space. Unfortunately, the passive sensors are unable to truly capture the theoretical displacements and will distort the measured signal $s(t)$ according to its instrument response $i_{k}(t)$.  In this study we consider the instrument response to include effects of the sensor, cabling and internal component of the data acquisition allowing for digitization of the signal.

@@

\section{Theory}
\label{theo}

We review the methodology that will model the forces produced by an active source piezoelectric transducer.  This methodology takes advantage of the theory surrounding elastodynamic wave propagation in an elastic medium.  We build on the recent studies of signal analysis and instrument calibration by \citet{McLaksey2012} continuing this analysis using Green's function formalization \citep{Aki2002, Johnson1974}. We assume that wave propagation can be adequately described by convolution with the Green's function and that each component in our analysis can be modeled as a linear-time invariant system.  We are assuming that changes in the sensor and source behavior and material properties are unaffected over time.  We assume point representations of both the sensor and source location. This so-called ``aperture'' effect is minimized by using the point contact conical PZT crystal but some deviations might be incurred.
